### 2015-10-29 config/glossaries.inc.tex
Update glossary a bit

%% SYMBOLS
\newsymbolglos{approx}{\approx}{Approximately equal}
\newsymbolglos{bydef}{\isdef}{Equal by definition}
\newsymbolglos{imagunit}{j}{The imaginary unit $j = \sqrt{-1}$}
\newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
\newsymbolglos{SetC}{\mathbb{C}}{Set of the complex numbers}
\newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\text{rad}/\text{s}$}
\newsymbolglos{f}{f}{Frequency in $\text{Hz}$}

%% ACRONYMS
\newacronym{vub}{VUB}{Vrije Universiteit Brussel}

\newacronym{siso}{SISO}{Single Input Single Output}
\newacronym{mimo}{MIMO}{Multiple Input Multiple Output}
\newacronym{bla}{BLA}{Best Linear Approximation}
\newacronym{frf}{FRF}{Frequency Response Function}
\newacronym{dut}{DUT}{Device Under Test}

\newacronym{FRF}{FRF}{frequency response function}
\newacronym{LTI}{LTI}{Linear time-invariant}

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LRIC}{LRIC}{Local Rational Method with Iterative Costfunction}

\newacronym{dft}{DFT}{Discrete Fourier Transform}
\newacronym{fft}{FFT}{Fast Fourier Transform}

>>>>

%% SYMBOLS
\newsymbolglos{approx}{\approx}{Approximately equal}
\newsymbolglos{bydef}{\isdef}{Equal by definition}
\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
\newsymbolglos{SetC}{\mathbb{C}}{Set of the complex numbers}
\newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\unit{rad/s}$}
\newsymbolglos{f}{f}{Frequency in $\unit{Hz}$}

%% ACRONYMS
\newacronym{VUB}{VUB}{Vrije Universiteit Brussel}

\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{SISO}{SISO}{Single Input Single Output}
\newacronym{MIMO}{MIMO}{Multiple Input Multiple Output}
\newacronym{SIMO}{SIMO}{Single Input Multiple Output}
\newacronym{MISO}{MISO}{Multiple Input Single Output}
\newacronym{BLA}{BLA}{Best Linear Approximation}
\newacronym{DUT}{DUT}{Device Under Test}

\newacronym{FRF}{FRF}{frequency response function}
\newacronym{LTI}{LTI}{Linear time-invariant}
\newacronym{ETFE}{ETFE}{Empirical Transfer Function Estimate}

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}

\newacronym{DFT}{DFT}{Discrete Fourier Transform}
\newacronym{FFT}{FFT}{Fast Fourier Transform}
